Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-02-26 index.qmd
first successful run of midline evo (fixed model)

---
title: "Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer"
authors:
  - name: Roman Ludwig
    orcid: 0000-0001-9434-328X
    email: roman.ludwig@usz.ch
  - name: Yoel Perez Haas
    email: yoel.perezhaas@usz.ch
  - name: Jan Unkelbach
    orcid: 0000-0002-4275-990X
    email: jan.unkelbach@usz.ch
format:
  html:
    code-fold: true
jupyter: python3
---

@@

```{python}
from lymph import models

graph_dict = {
  ("tumor", "T"): ["II", "III"],
  ("lnl", "II"): ["III"],
  ("lnl", "III"): [],
}
model = models.Midline(
  graph_dict=graph_dict,
  is_symmetric={"lnl_spread": True},
  use_mixing=True,
  use_central=False,
  use_midext_evo=True,
)
model.set_modality("max_llh", spec=1.0, sens=1.0)
```

>>>>

---
title: "Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer"
authors:
  - name: Roman Ludwig
    orcid: 0000-0001-9434-328X
    email: roman.ludwig@usz.ch
  - name: Yoel Perez Haas
    email: yoel.perezhaas@usz.ch
  - name: Jan Unkelbach
    orcid: 0000-0002-4275-990X
    email: jan.unkelbach@usz.ch
format:
  html:
    code-fold: true
jupyter: python3
execute: 
  cache: true
---

@@

# Methods

# Results

```{python}
from emcee import backends
from corner import corner
import matplotlib.pyplot as plt
from tueplots import figsizes, fontsizes

backend = backends.HDFBackend(
  filename="models/midline_fix.hdf5",
  read_only=True,
)
samples = backend.get_chain(thin=20)
ndim = samples.shape[-1]

plt.rcParams.update(**figsizes.icml2022_full(nrows=ndim))

fig, axes = plt.subplots(nrows=ndim, sharex=True)
for i, ax in enumerate(axes):
  ax.plot(samples[:,::10,i], color="gray", alpha=0.2)
  ax.axhline(samples[200:,:,i].mean(), color="red")
  ax.set_xlim(0., samples.shape[0])
  ax.set_ylim(0., 1.)
```
